\begin{originality}
  This synopsis outlines the work from the following conference publications:
  \begin{enumerate}
  \item Kumar Madhukar, Mandayam Srivas, Bj\"{o}rn Wachter, Daniel Kroening,
and Ravindra Metta. 2015. Verifying synchronous reactive systems using lazy
abstraction. In Proceedings of the 2015 Design, Automation \& Test in Europe
Conference \& Exhibition (DATE '15). EDA Consortium, San Jose, CA, USA,
1571-1574.

  \item Kumar Madhukar, Bj\"{o}rn Wachter, Daniel Kroening, Matt Lewis, and
Mandayam K. Srivas. Accelerating invariant generation. In Roope Kaivola and
Thomas Wahl, editors, Formal Methods in Computer-Aided Design, FMCAD 2015,
Austin, Texas, USA, September 27-30, 2015., pages 105-111. IEEE, 2015.
  \end{enumerate}

  I was the lead investigator for the work in both. These studies were
conceived and developed jointly by Bj\"{o}rn Wachter, Mandayam Srivas and me.
The implementation and experiments for both (1) and (2) was carried out by me,
with significant guidance from Bj\"{o}rn Wachter, in a framework which has been
developed by Bj\"{o}rn Wachter and Daniel Kroening. I was primarily responsible
for the writing of the manuscripts, to which all other authors made significant
contributions.

  This synopsis also summarizes some unpublished work that has been carried out
in the last few months. The ideas, implementation and experiments for this work
have been developed and carried out jointly by Peter Schrammel and myself.
Peter Schrammel is a Lecturer in Computer Science at the University of Sussex
in Brighton (UK) since March 2016. Earlier, he was a Research Assistant in the
Department of Computer Science at the University of Oxford. The implementation
framework has been developed by Peter Schrammel and Daniel Kroening. Mandayam
Srivas and Daniel Kroening have helped in refining the ideas through several
discussions. A paper on this is currently under review at SAS 2016.
  
\end{originality}
